%!TEX root = ../todd-cv.tex
%----------------------------------------------------------------------------------
%            Funding
%----------------------------------------------------------------------------------
\section{Research and Other Funding}
\cventry{2023-2028}
		{Co-PI}
		{PESO: Post-ECP Sustainability Organization}
        {PI Mike Heroux}{}
	{Part of DOE Advanced Scientific Computing Research (ASCR) Software Stewardship Program.
          Aims to steward and advance the DOE HPC software stack.
          \$4M/year.}
\cventry{2016-present}
		{PI}
		{DevRAMP: Reproducibility, Analysis, Monitoring, and Performance for Developers}
        {}{Programmatic, \$1.4M/year}
		{Department of Energy (DOE) Advanced Simulation and Computing (ASC) Program.}
\cventry{2020-2023}
		{PI}
		{BUILD: Binary Understanding and Integration Logic for Dependencies}
        {}{LLNL Strategic Initiative}
		{Laboratory Directed Research and Development (LDRD) Program, \$2.3M/year.}
\cventry{2019-2023}
		{PI}
		{Packagng Technologies Project.}
        {}{Programmatic, \$1.9M/year}
		{Exascale Computing Project, L4 project.}
\cventry{2017-2018}
		{PI}
		{LLNL Early and Mid-Career Recognition Award}{}{20\% time}
		{Recognized by LLNL and funded to work on expanding the Spack community.}
\cventry{2017-2019}
		{Co-PI}
		{IDEAS-ECP: Softare Productivity for the Exascale Computing Project}
        {PIs Mike Heroux and Lois Curfman McInnes}{\$225k/yr}
		{U.S. Exascale Computing Project}
\cventry{2014-2019}
		{PI}
		{Statistical Methods for Exascale Performance Modeling}{}{\$2,500,000}
		{U.S. Department of Energy (DOE) Early Career Research Program.}
\cventry{2010-2019}
		{PI}
		{Performance Analysis and Visualization at Exascale (PAVE)}{}{\$500K/year}
		{%Proposed as Lab Directed Research and Development (LDRD), funded
		 %programmatically under\newline
		 Department of Energy (DOE) Advanced Simulation and Computing (ASC) Program.}
\cventry{2015-2016}
		{PI}
		{Containers and Secure Services for HPC}
        {}{\$100k}
		{LLNL ISCP Project}
\cventry{2014-2017}
		{PI}
		{Sonar: An Analytics Cluster for Livermore Computing Performance Data}{}{\$100k/yr}
		{LLNL Computation TechBase Project}
\cventry{2013-2015}
		{Co-PI}
		{Performance Insight for Programs and Exascale Runtimes (PIPER)}{}{\$4.5M}
		{PI Martin Schulz, LLNL. DOE Advanced Scientific Computing Research (ASCR)
		 X-Stack 2 Program.}
\cventry{2012-2014}
		{Co-PI}
		{Performance Visualization at ExaScale (PeVES)}{}{\$250k}
		{PI Timo Bremer, LLNL. University of California Laboratory Fees Research Program.}
\cventry{2012-2014}
		{Co-PI}
		{Scalable Topology-Aware Task Embedding (STATE)}{}{\$945k}
		{PI Abhinav Bhatele, LLNL. DOE LDRD Exploratory Research.}
\cventry{2012}
		{PI}
		{Data Analytics for HPC}{}{\$100k}
%		{DOE LDRD Feasibility Study.}
		{}
