%!TEX root = ../todd-cv.tex
%----------------------------------------------------------------------------------
%            Professional Activities (Long)
%----------------------------------------------------------------------------------
\section{Conferences \& Workshops Organized}
        \cventry{2021, 2023}
            {PackagingCon}
            {Co-Chair, Co-Founder}{}{}
            {2021: Virtual Event, 350+ attendees; }
        \cventry{2017}
            {IEEE CLUSTER}
            {General Chair}{}{}
            {Honolulu, Hawaii, 180+ attendees}
	\cventry{2014-2016}
		{JOWOG 34: Applied Computer Science}
		{Co-Chair, Co-Founder}
		{}{}
		{Scalable algorithms \& simulation techniques for
		  LLNL, LANL, Sandia (US) and AWE (UK).  100+ attendees.\newline
                  Continues to be held yearly.
                }
	\cventry{2015-2016}
		{International Workshop on HPC User Support Tools (HUST)}
		{Co-Chair}{}{}
		{Held at SC15-present in cooperation with SIGHPC.}
	\cventry{2016}
		{Workshop on Variability in Parallel and Distributed Systems (VarSys)}
		{Co-Chair}{}{}
		{Held at IPDPS'16.}
	\cventry{2016}
                {Workshop on Emerging Parallel and Distributed Runtime Systems and Middleware\newline
                 (IPDRM'16)}
		{Co-Chair}{}{}
		{Held at IPDPS'16-17 and SC'20.}
	\cventry{2011-2012}
		{Workshop on High-performance Infrastructure for Scalable Tools (WHIST)}
		{Chair}{}{}
		{Held twice at ICS. Proceedings published in special issue of ParCo Journal. 30 attendees.}


\section{Conference Committees}
	\cventry{2025}{ACM/IEEE Supercomputing Conference (SC25)}
		{System Software and Cloud Computing Track}{}{}{}
	\cventry{2023}{ACM/IEEE Supercomputing Conference (SC23)}
		{Performance Track, Test of Time Award Comittee Member}{}{}{}
	\cventry{2021}{ACM/IEEE Supercomputing Conference (SC21)}
		{Technical Program Vice Chair}{}{}{}
	\cventry{2019}{ACM/IEEE Supercomputing Conference (SC19)}
		{Technical Papers Committee}{}{}{}
	\cventry{2019}{ACM Symp. on Principles and Practices of Parallel Programming (PPoPP)}
		{Finance Chair}{}{}{}
	\cventry{2018}{ACM/IEEE Supercomputing Conference (SC18)}
		{Vice Chair, Technical Papers}{}{}{}
	\cventry{2017}{ACM/IEEE Supercomputing Conference (SC17)}
		{Posters Committee}{}{}{}
    \cventry{2017}{Parallel Architectures and Compilation Techniques (PACT)}
        {Technical Papers Committee}{}{}{}
	\cventry{2014-2017}{International Workshop on HPC User Support Tools (HUST)}
		{Technical Papers}{}{}{}
	\cventry{2014-2017}{International Workshop on Visual Performance Analytics (VPA)}
		{Technical Papers}{}{}{}
    \cventry{2016}{International Conference on Parallel Processing (ICPP)}{Technical Papers Committee}{}{}{}
	\cventry{2012-2016}{ACM Student Research Competition}
		{Review Committee}{}{}{}
	\cventry{2010-2016}
		{Performance Modeling, Benchmarking, \& Simulation (PMBS)}
		{Steering Committee}{}{}{}
	\cventry{2015}{IEEE CLUSTER}
		{Area Chair, Cluster Design and Architecture}{}{}{}
	\cventry{2015}{PPoPP 2015}
		{External Program Committee}{}{}{}
	\cventry{2013,2014}{ACM/IEEE Supercomputing Conference (SC13,SC14)}
		{Technical Papers Committee}{}{}{}
	\cventry{2011,2014}{ACM International Conference on Supercomputing (ICS)}
		{Technical Papers Committee}{}{}{}
	\cventry{2014}{IEEE International Parallel and Distributed Processing
		Symposium (IPDPS)}{Tech. Papers}{}{}{}
	\cventry{2014}{Hardware-Software Co-Design for High Performance Computing (Co-HPC)}
		{Technical Papers Committee}{}{}{}
	\cventry{2013-2014}{IEEE/ACM Cluster, Cloud \&Grid Computing (CCGrid)}
		{Technical Papers Committee}{}{}{}
	\cventry{2013-2014}{IEEE Big Data}
		{Technical Papers Committee}{}{}{}
	\cventry{2012-2013}{International Conference on Parallel Processing (ICPP)}
		{Technical Papers Committee}{}{}{}
	\cventry{2012}{IEEE CLUSTER}
		{Technical Papers Committee}{}{}{}
	\cventry{2012}{ACM/IEEE Supercomputing Conference (SC)}
		{Posters Committee}{}{}{}
    \cventry{2009}{Parallel Architectures and Compilation Techniques (PACT)}
        {Web Chair}{}{}{}

\section{Grant Reviewing}
	\cventry{2021}{Small Business Innovation Research (SBIR)}{DOE Office of Science}{}{}{}
	\cventry{2019}{Predictive Science Academic Alliance Program (PSAAP III)}{DOE NNSA}{}{}{}
	\cventry{2015}{Computing and Communication Foundations (CCF)}{NSF}{}{}{}
	\cventry{2012}{Predictive Science Academic Alliance Program (PSAAP II)}{DOE NNSA}{}{}{}
	\cventry{2011}{Small Business Innovation Research (SBIR)}{DOE Office of Science}{}{}{}

\section{Memberships}
    \cvitem{Professional}{
      \href{http://www.ieee.org}{IEEE},
      \href{http://www.acm.org/}{ACM},
      \href{http://sighpc.org/}{SIGHPC}
    }
    \cvitem{Teaching}{
      \href{https://software-carpentry.org/}{Software Carpentry} Certified Instructor
    }
    \cvitem{Open Source}{
      \href{http://openhpc.community/}{OpenHPC} Techical Steering Committee (Developer Tools Representative)
    }
