%!TEX root = ../todd-cv.tex
%----------------------------------------------------------------------------------
%        Research Experience
%----------------------------------------------------------------------------------
\section{Research Experience}
	\cventry{2010-present}
		{Computer Scientist}
		{\href{http://www.llnl.gov}{Lawrence Livermore National Laboratory}}{}{}
		{As team leader for the Performance Analysis and Visualization at Exascale (PAVE) project,
		 investigating more intuitive ways to visualize and analyze performance data.
		 On the Exascale Computing Technologies (ExaCT) Strategic Initiative and on SciDAC SUPER project, researching
		 scalable performance tools for machines with millions of cores.  Projects include Muster, a library for
		 massively clustering massively distributed data sets; Libra, a scalable load balance analysis tool, and
		 other HPC performance tool projects.  In spare time, deploying collaboration tools for software developers.}

	\cventry{2009-2010}
		{Postdoctoral Scholar}
		{\href{http://www.llnl.gov}{Lawrence Livermore National Laboratory}}{}{}
		{Developed $O(log(P))$ clustering algorithm for on-line analysis in parallel tools.
		 Developed optimizations for stack tracing library using stack smashing instrumentation.  Researched techniques for
		 scalable performance analysis as part of ExaCT project.  Led initial HPC thrust
		 of strategic power grid modeling project.}

	\cventry{2008-2009\\Jun, Aug 2007}
		{Research Intern}
		{\href{http://www.llnl.gov}{Lawrence Livermore National Laboratory}}{}{}
		{Collaborated with Bronis de Supinski on scalable load-balance measurement and Ph.D. dissertation.}

	\cventry{2004-2008}
		{Research Assistant}
		{\href{http://www.renci.org}{Renaissance Computing Institute (RENCI)}, UNC Chapel Hill}{}{}
		{Built load-balance tools using wavelet compression.  Researched clustering performance data and adaptively sampled tracing.  Worked towards Ph.D. on scalable performance monitoring, advised by Daniel A. Reed.}

	\cventry{Summer 2006}
		{Research Intern}
		{\href{http://www.watson.ibm.com}{IBM Thomas J. Watson Research Center}}{}{}
		{Worked with Dr. Alan Bivens on on distributed clock synchronization algorithms for virtualized environments.  Adapted a synchronization algorithm used in System z mainframes for use in Java environments.}

	\cventry{Summer 2004}
		{Research Intern}
		{\href{http://www.hal.rcast.u-tokyo.ac.jp/}{Nanya-Nakamura Laboratory}, University of Tokyo}{}{}
		{On NSF EAPSI fellowship, investigated building low-power processors with asynchronous digital logic.}

	\cventry{2003-2004}
		{Research Assistant}
		{\href{http://www.cs.unc.edu/~montek/}{Clockless Computing}, UNC Chapel Hill}{}{}
		{Investigated modular interfaces for asynchronous circuits with Dr. Montek Singh.}

	\cventry{2001-2002}
		{Undergraduate Research Assistant}
		{\href{http://www.williams.edu}{Williams College}}{}{}
		{Project on cache-conscious memory optimizations.  Worked with Dr. Duane A. Bailey.}

	\cventry{Summer 1999}
		{Summer Research Assistant}
		{\href{http://physics.ncsu.edu/}{NCSU Physics Department}}{}{}
		{Designed imaging algorithms and an archival website for the Diffraction Enhanced Imaging Group.}
