%!TEX root = ../grant-cv.tex
%----------------------------------------------------------------------------------
%            Professional Activities
%----------------------------------------------------------------------------------
\section{Conferences \& Workshops Organized}
    \cventry{2017}
        {IEEE CLUSTER}
        {General Chair}
        {}{}{}
%        {Location to be announced at IEEE CLUSTER 2016}
	\cventry{2014-2016}
		{JOWOG 34: Applied Computer Science}
		{Co-Chair \& Founder}
		{NNSA US/UK Meeting}{}{}
	\cventry{2015-2016}
		{International Workshop on HPC User Support Tools (HUST)}
		{Co-Chair}{Held at SC'15-16}{}{}
	\cventry{2016}
		{Workshop on Variability in Par. \& Distrib. Systems}
		{Co-Chair}{At IPDPS'16.}{}{}
	\cventry{2016}
		{Workshop on Par. \& Distrib. Runtimes and Middleware (IPDRM)}
		{Co-Chair}{At IPDPS'16.}{}{}
	\cventry{2011-2012}
		{Workshop on High-perf. Infrastructure for Scalable Tools (WHIST)}
		{Chair}{Held at ICS}{}{}{}

\section{Committees}
	\cvitem{Technical Program Committees}{
		Supercomputing (SC) '13,'14. SC'12 (Posters). ICS'11,'14. IPDPS'14.
		CCGrid '13,'14. \newline
		ICPP '12,'13,'16. IEEE CLUSTER'12,'14,'15 (Area chair). 
		ACM SRC '12,'13. HUST'14--'16.  PMBS'10--'15.
		EuroMPI '17.
		IEEE Big Data '13,'14.
	}
	\cvitem{Grant Review Committees}{
		NNSA Predictive Science Academic Alliance Program (PSAAP II), 2012.\newline
		DOE Small Business Innovation Research (SBIR) 2011.
	}
	\cvitem{Steering Cmte.}{
		Int. Workshop on Performance Modeling, Benchmarking, and Simulation (PMBS) 2010--14
	}
	\cvitem{Organizing Cmte.}{
		Parallel Architectures and Compilation Techniques (PACT) 2009
	}
	\cvitem{Other Reviewing}{
		IEEE TPDS, ParCo, IJHPCA, Computer Journal, ISPASS'10, IPDPS'09, ICS'09, PACT'09}
	\cvitem{Memberships}{
		\href{http://www.ieee.org}{IEEE}, \href{http://www.acm.org/}{ACM}, 
		\href{http://sighpc.org/}{SIGHPC}
	}
